False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2016-03-07 document/ms.tex
tables updated

\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize}
\tablecaption{\vespa--calculated FPPs of the \\Santerne (2015) RV sample
  \tablabel{santerne}}
\tablehead{\colhead{RV-based nature} & \colhead{mean FPP} & \colhead{median FPP}}
\startdata
Planet & 0.0892 & 0.0002 \\
Brown dwarf & 0.0035 & 0.0038 \\
Eclipsing binary (EB) & 0.7764 & 0.9450 \\
Contaminating EB & 0.8326 & 0.9950 \\
Undetermined & 0.2393 & 0.0032
\enddata
\end{deluxetable}

>>>>

\input{table_santerne}
